\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-03-22 journalSwarmControl/IJRR Archive/realExperiment.tex
First round on TASE paper (format, changes)

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std). 
A circular object completed in 3155 s.    
A square object completed in 6871 s. 
A rectangle and three equilateral triangle objects of varying sizes failed in a total of nine runs.  Failures occurred when the object was pushed into a corner, requiring torque to be unstuck.  This paper focuses on force, but not torque control. Swarm torque control is the subject of ongoing research in \cite{Shahrokhi2016CASE}.

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(48,8){\emph{t} = 2185 s}\put(80,8){\emph{t} = 2703 s}
\end{overpic}
%\vspace{-1em}
\caption{\label{fig:expSnapShot}Snapshots showing object manipulation experiment with 100 kilobots under automatic control. The automatic controller generates a policy to the goal. See  supplementary material video 2.}
        \end{figure}

>>>>

The kilobots performed five successful runs of object manipulation through the obstacle maze, see Extension 2.
Each trial used 100 kilobots. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std). 
A circular object completed in 3155 s.    
A square object completed in 6871 s. 
A rectangle and three equilateral triangle objects of varying sizes failed in a total of nine runs.  Failures occurred when the object was pushed into a corner, requiring torque to be unstuck.  This paper focuses on force, but not torque control. Swarm torque control is the subject of ongoing research in \cite{Shahrokhi2016CASE}.

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(48,8){\emph{t} = 2185 s}\put(80,8){\emph{t} = 2703 s}
\end{overpic}
%\vspace{-1em}
\caption{\label{fig:expSnapShot}Snapshots showing object manipulation experiment with 100 kilobots under automatic control. The automatic controller generates a policy to the goal, (see Extension 2).}
        \end{figure}

### 2017-03-22 journalSwarmControl/Introduction.tex
changed order of video numbers
The submitted version.
First round on TASE paper (format, changes)

%Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges to generating controlled motion.  
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Limited computation and communication rules out autonomous operation or direct control over individual units; instead we must rely on global control signals broadcast to the entire robot population.  Additionally, many promising applications will require direct human control, but user interfaces to thousands---or millions---of robots is a daunting human-swarm interaction (HSI) challenge.

Our previous work with over a hundred hardware robots and thousands of simulated robots demonstrated that direct human control of large swarms is possible, \cite{Becker2013b}. 
Unfortunately, the logistical challenges of repeated experiments with over one hundred robots prevented large-scale tests. 
There is currently no comprehensive understanding of user interfaces for controlling multi-robot systems with massive populations.  
This paper presents a tool for investigating HSI methods through statistically significant numbers of experiments.

\begin{figure}
\centering
\renewcommand{\figwid}{0.3\columnwidth}
\begin{overpic}[width =\figwid]{VaryNum.pdf}	\put(10,80){\textbf{a} }\end{overpic}~
\begin{overpic}[width =\figwid]{VaryVisMV.pdf}	\put(10,80){\textbf{b} }\end{overpic}~
\begin{overpic}[width =\figwid]{VaryNoise.pdf}	\put(10,80){\textbf{c} }\end{overpic}\\
\begin{overpic}[width =\figwid]{ControlPos.pdf}	\put(10,80){\textbf{d} }\end{overpic}~
\begin{overpic}[width =\figwid]{VaryControl.pdf}	\put(10,80){\textbf{e} }\end{overpic}~
\begin{overpic}[width =\figwid]{VaryForage.pdf}	\put(10,80){\textbf{f} }\end{overpic}
\caption{\label{fig:5experiments}
Screenshots from our online experiments controlling multi-robot systems with limited, global control.
\textbf{(a)} Varying the number of robots from 1-500
\textbf{(b)} Comparing 4 levels of visual feedback 
\textbf{(c)} Varying noise from 0 to 200\% of control authority
\textbf{(d)} Controlling the position of 1 to 10 robots
\textbf{(e)} Comparing 3 control architectures to assemble
\textbf{(f)} Comparing 3 control architectures to forage.
}
\end{figure}

@@

Our online experiments show that numerous simple robots responding to global control inputs are directly controllable by a human operator without special training, that the visual feedback of the swarm state should be simple to increase task performance, and that humans perform swarm-object manipulation faster using attractive control schemes than repulsive control schemes.

%Inspired by our online experiments, because it is not always possible to gather pose information on each robot for feedback control and
%It is not always practical to gather pose information on individual robots for feedback control; the robots might be difficult or impossible to sense individually due to their size and location. However, it is often possible to sense global properties of the group, such as mean position and density.
Often robots are difficult or impossible to sense individually due to their size and location. 
For example, microrobots are smaller than the minimum resolution of a clinical MRI-scanner, see \cite{martel2014computer}, however it is often possible to sense global properties of the group, such as mean position and variance. 
To make progress in automatic control with global inputs, this paper presents swarm manipulation controllers, inspired by our online experiments, that require only mean and variance measurements of the robot's positions.  
These controllers are used as primitives to perform the object manipulation task illustrated in Fig.~\ref{fig:bigPictureMeanAndVarianceForSwarm}.

\begin{figure}
\centering
%\begin{overpic}[height=6cm]{CompleteMazeDescription.pdf}\end{overpic}
\begin{overpic}[width=\columnwidth]{MainExpFig.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} A swarm of robots, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the mean and variance of the robot distribution.  Here a swarm of robots pushes a green hexagon toward the goal. 
%Simulation at left, screen capture from hardware experiment at right. 
See video 1 in supplemental materials.}
\end{figure}
 %function and implementation function

 Our paper is organized as follows.  After a discussion of related work in \S \ref{sec:RelatedWork},  we describe our experimental methods for an online human-user experiment in \S \ref{sec:expMethods}. We report the results of our online experiments in \S \ref{sec:expResults}. Inspired by these results, we prove that the mean and variance of a robot swarm are controllable in \S \ref{sec:theory}, and present automatic controllers in \S \ref{sec:simulation}. We use these controllers as primitives and present a framework for manipulating an object through a maze in \S \ref{sec:exp}. 
 We conclude with implementations of these controllers in our hardware robots and use them to complete an object manipulation task with 100 kilobots in \S \ref{sec:realExperiment}.

>>>>

%Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges to generating controlled motion.  
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Limited computation and communication rules out autonomous operation or direct control over individual units; instead we must rely on global control signals broadcast to the entire particle population.  Additionally, many promising applications will require direct human control, but user interfaces to thousands---or millions---of particles is a daunting human-swarm interaction (HSI) challenge.

Our previous work with over a hundred hardware robots and thousands of simulated particles demonstrated that direct human control of large swarms is possible, \cite{Becker2013b}. 
Unfortunately, the logistical challenges of repeated experiments with over one hundred robots prevented large-scale tests. 
There is currently no comprehensive understanding of user interfaces for controlling multi-robot systems with massive populations.  
This paper presents a tool for investigating HSI methods through statistically significant numbers of experiments.

\begin{figure}
\centering
%\begin{overpic}[height=6cm]{CompleteMazeDescription.pdf}\end{overpic}
\begin{overpic}[width=\columnwidth]{MainExpFig.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} A swarm of particles, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the mean and variance of the robot distribution.  Here a swarm of particles pushes a green hexagon toward the goal 
%Simulation at left, screen capture from hardware experiment at right. 
(see also Extension 2).}
\end{figure}

\begin{figure}
%\centering
\renewcommand{\figwid}{0.3\columnwidth}
\begin{overpic}[width =\figwid]{VaryNum.pdf}	\put(10,80){\textbf{a} }\end{overpic}~
\begin{overpic}[width =\figwid]{VaryVisMV.pdf}	\put(10,80){\textbf{b} }\end{overpic}~
\begin{overpic}[width =\figwid]{VaryNoise.pdf}	\put(10,80){\textbf{c} }\end{overpic}\\
\\
\begin{overpic}[width =\figwid]{ControlPos.pdf}	\put(10,80){\textbf{d} }\end{overpic}~
\begin{overpic}[width =\figwid]{VaryControl.pdf}	\put(10,80){\textbf{e} }\end{overpic}~
\begin{overpic}[width =\figwid]{VaryForage.pdf}	\put(10,80){\textbf{f} }\end{overpic}
\caption{\label{fig:5experiments}
Screenshots from our online experiments controlling multi-particle systems with limited, global control.
\textbf{(a)} Varying the number of particles from 1-500
\textbf{(b)} Comparing 4 levels of visual feedback 
\textbf{(c)} Varying noise from 0 to 200\% of control authority
\textbf{(d)} Controlling the position of 1 to 10 particles
\textbf{(e)} Comparing 3 control architectures to assemble
\textbf{(f)} Comparing 3 control architectures to forage.
}
\end{figure}

@@

Our online experiments show that numerous particles responding to global control inputs are directly controllable by a human operator without special training, that the visual feedback of the swarm state should be simple to increase task performance, and that humans perform swarm-object manipulation faster using attractive control schemes than repulsive control schemes.

%Inspired by our online experiments, because it is not always possible to gather pose information on each robot for feedback control and
%It is not always practical to gather pose information on individual robots for feedback control; the robots might be difficult or impossible to sense individually due to their size and location. However, it is often possible to sense global properties of the group, such as mean position and density.
Often particles are difficult or impossible to sense individually due to their size and location. 
For example, microrobots are smaller than the minimum resolution of a clinical MRI-scanner, see \cite{martel2014computer}, however it is often possible to sense global properties of the group, such as mean position and variance. 
To make progress in automatic control with global inputs, this paper presents swarm manipulation controllers, inspired by our online experiments, that require only mean and variance measurements of the particle's positions.  
These controllers are used as primitives to perform the object manipulation task illustrated in Fig.~\ref{fig:bigPictureMeanAndVarianceForSwarm}.

 %function and implementation function

 Our paper is organized as follows.  After a discussion of related work in \S \ref{sec:RelatedWork},  we describe our experimental methods for an online human-user experiment in \S \ref{sec:expMethods}. We report the results of our online experiments in \S \ref{sec:expResults}. Inspired by these results, we prove that the mean and variance of a particle swarm are controllable in \S \ref{sec:theory}, and present automatic controllers in \S \ref{sec:simulation}. We use these controllers as primitives and present a framework for manipulating an object through a maze in \S \ref{sec:exp}. 
 We conclude with implementations of these controllers in our hardware robots and use them to complete an object manipulation task with 100 kilobots in \S \ref{sec:realExperiment}.

### 2017-03-22 journalSwarmControl/TASE/SwarmControlIJRR.tex
First round on TASE paper (format, changes)

% compress:
% gs -sDEVICE=pdfwrite -dCompatibilityLevel=1.4 -dNOPAUSE -dQUIET -dBATCH      -sOutputFile=CompressedSwarmControlIJRR.pdf SwarmControlIJRR.pdf
%%%%%%%%% IJRR SETTINGS
%  from https://us.sagepub.com/en-us/nam/manuscript-submission-guidelines#PreparingYourManuscript
\documentclass[Afour,sageh,times]{sagej} % sage_latex_guidelines.tex V1.01, 11 June 2015
\usepackage{moreverb,url}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=black,urlcolor=black,linkcolor = black]{hyperref}
\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\def\volumeyear{2016}
%%%%%%%%%%%% END IJRR SETTINGS
\def\journalname{The International Journal of Robotics Research}
% How many words:  $ detex IJRRensembleDifferentialDrive.tex | wc -w

%\usepackage[pdftex]{graphicx}        % standard LaTeX graphics tool
%\usepackage[usenames,dvipsnames]{color}
\usepackage{calc}
\usepackage{graphicx}
%\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{color}
\usepackage{colortbl} %TODO: lab computers choke on this.  Why?
%\usepackage{cite}
%\usepackage[font={small}]{caption}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{overpic}
\graphicspath{{./},{./pictures/pdf/},{./pictures/ps/},{./pictures/png/},{./pictures/jpg/}}
\usepackage{breqn} %for breaking equations automatically
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
%\usepackage{algorithmic}
\usepackage{bm}   % boldface math type
\usepackage{upgreek}   % non-slanted greek letters
\usepackage{soul} %for highlighting

%\usepackage[round]{natbib}
\usepackage{mathtools}
%\usepackage{authblk}
\usepackage{wrapfig}

%% ABBREVIATIONS
\newcommand{\todo}[1]{\textcolor{red}{\footnotesize \textsf{#1}}}
\newcommand\mydefeq{\stackrel{\mathclap{\normalfont\mbox{\tiny def}}}{=}}
\newcommand{\qstart}{\mathbf{q}_{\text{start}}}
\newcommand{\qgoal}{\mathbf{q}_{\text{goal}}}
\newcommand{\pstart}{\mathbf{p}_{\text{start}}}
\newcommand{\pgoal}{\mathbf{p}_{\text{goal}}}
\newcommand{\xstart}{x_{\text{start}}}
\newcommand{\xgoal}{x_{\text{goal}}}
\newcommand{\ystart}{y_{\text{start}}}
\newcommand{\ygoal}{y_{\text{goal}}}
\newcommand{\gammastart}{\gamma_{\text{start}}}
\newcommand{\gammagoal}{\gamma_{\text{goal}}}
\newcommand{\CM}{\textsc{cm}}
\newcommand{\SVM}{\textsc{svm}}
\newcommand{\NN}{\textsc{nn}}
\newcommand{\prm}{\textsc{prm}}
\newcommand{\lemur}{\textsc{lemur}}
\newcommand{\Lemur}{\textsc{Lemur}}
\newcommand{\LP}{\textsc{lp}} 
\newcommand{\SOCP}{\textsc{socp}}
\newcommand{\SDP}{\textsc{sdp}}
\newcommand{\NP}{\textsc{np}}
\newcommand{\SAT}{\textsc{sat}}
\newcommand{\LMI}{\textsc{lmi}}
\newcommand{\hrp}{\textsc{hrp\nobreakdash-2}}
\newcommand{\DOF}{\textsc{dof}}
\newcommand{\UIUC}{\textsc{uiuc}}
\newcommand{\Cspace}{\mathcal{Q}}
\newcommand{\Uspace}{\mathcal{U}}
\newcommand{\D}{\nobreakdash-\textsc{d}}
\newcommand{\contact}[1]{\Cspace_{#1}}
\newcommand{\feasible}[1]{\Fspace_{#1}}
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\ii}{{\rm i}}
\newcommand{\TRUE}{\textbf{true}}
\newcommand{\FALSE}{\textbf{false}}

\newcommand{\figwid}{0.22\columnwidth}
%\newcommand{\topic}[1]{\textcolor{ForestGreen}{\footnotesize \textsf{#1}}}
%\newcommand{\todo}[1]{\textcolor{red}{\footnotesize \textsf{#1}}}

%% MACROS
\providecommand{\proc}[1]{\textsc{#1}}
\providecommand{\ddelta}{\underline{\bm{\updelta}}}  % requires \usepackage{bm,upgreek}
\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\providecommand{\normn}[2]{\left\lVert#1\right\rVert_#2}
\providecommand{\dualnorm}[1]{\norm{#1}_\ast}
\providecommand{\dualnormn}[2]{\norm{#1}_{#2\ast}}
\providecommand{\set}[1]{\lbrace\,#1\,\rbrace}
\providecommand{\cset}[2]{\lbrace\,{#1}\nobreak\mid\nobreak{#2}\,\rbrace}
\providecommand{\lscal}{<}
\providecommand{\gscal}{>}
\providecommand{\lvect}{\prec}
\providecommand{\gvect}{\succ}
\providecommand{\leqscal}{\leq}
\providecommand{\geqscal}{\geq}
\providecommand{\leqvect}{\preceq}
\providecommand{\geqvect}{\succeq}
\providecommand{\onevect}{\mathbf{1}}
\providecommand{\zerovect}{\mathbf{0}}
\providecommand{\field}[1]{\mathbb{#1}}
\providecommand{\C}{\field{C}}
\providecommand{\R}{\field{R}}
\providecommand{\Fspace}{\Cspace_\text{free}}
\providecommand{\Hcal}{$\mathcal{H}$}
\providecommand{\Vcal}{$\mathcal{V}$}
\providecommand{\polar}{\triangle}
\providecommand{\ainner}{\underline{a}}
\providecommand{\aouter}{\overline{a}}
\providecommand{\binner}{\underline{b}}
\providecommand{\bouter}{\overline{b}}
\providecommand{\Fspace}{\Cspace_\text{free}}
\providecommand{\free}{\text{\{}\mathsf{free}\text{\}}}
\providecommand{\iff}{\Leftrightarrow}
\providecommand{\subinner}[1]{#1_{\text{inner}}}
\providecommand{\subouter}[1]{#1_{\text{outer}}}
\providecommand{\Ppoly}{\mathcal{X}}
\providecommand{\Pproj}{\mathcal{Y}}
\providecommand{\Pinner}{\subinner{\Pproj}}
\providecommand{\Pouter}{\subouter{\Pproj}}
\providecommand{\Aineq}{B}
\providecommand{\Aeq}{A}
\providecommand{\bineq}{u}
\providecommand{\beq}{t}

\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\cone}{cone}
\DeclareMathOperator{\homog}{homog}
\DeclareMathOperator{\domain}{dom}
\DeclareMathOperator{\range}{range}
\DeclareMathOperator{\sign}{sgn} 
\DeclareMathOperator{\argmax}{arg\,max}
\DeclareMathOperator{\area}{area}
\DeclareMathOperator{\atan2}{atan2}
\DeclareMathOperator*{\argmax2}{argmax}

@@

\begin{document}
\setcounter{secnumdepth}{3}
\runninghead{Shahrokhi \textit{et~al.}}
\hyphenation{micro-robot nano-robot nano-robotics micro-robotics micro-robots nano-robots micro-manip-ulators}
%%%%%%%%%%%% For debugging purposes, I like to display the TOC
%    \tableofcontents
%    \setcounter{tocdepth}{3}
%    \newpage
%%%% END TOC %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{Shiva Shahrokhi, Chris Ertel, Mable Wan, Lillian Lin, Aaron T. Becker}% end author block 
\affiliation{Electrical and Computer Engineering, University of Houston, USA}
\corrauth{Shiva Shahrokhi,
University of Houston,
4726 Calhoun Rd,
Houston, TX 77004-4005, USA}
\email{sshahrokhi2@uh.edu}

\begin{abstract}
Microrobotics has the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges for controlling motion. We want to use large swarms of robots to perform manipulation tasks; unfortunately, human-swarm interaction studies as conducted today are limited in sample size, are difficult to reproduce, and are prone to hardware failures. We present an alternative.

@@

\keywords{micro-robot, global control, swarm, human-swarm interaction}

\maketitle

@@

\begin{dci}
The Authors declare that there is no conflict of interest.
\end{dci}
\begin{funding}
%RULES: http://www.nsf.gov/pubs/policydocs/pappguide/nsf16001/aag_6.jsp
This work was supported by the National Science Foundation under Grant No.\ 
\href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}.
\end{funding}
\newpage
\begin{sm}
\begin{itemize}
\item Extension 1:  simulation video of the parameter sweeps in Fig.~\ref{fig:AutoVeryParam} with robot swarms manipulating objects.
\item Extension 2: hardware experiment videos of object manipulation with a swarm of 100 kilobots.
\end{itemize}
\end{sm}

@@

%\bibliographystyle{IEEEtran}
\bibliographystyle{SageH}
\bibliography{IEEEabrv,SwarmControlIJRR}

>>>>

% compress:
% gs -sDEVICE=pdfwrite -dCompatibilityLevel=1.4 -dNOPAUSE -dQUIET -dBATCH      -sOutputFile=CompressedSwarmControlIJRR.pdf SwarmControlIJRR.pdf
%%%%%%%%% IJRR SETTINGS
%  from https://us.sagepub.com/en-us/nam/manuscript-submission-guidelines#PreparingYourManuscript
%\documentclass[Afour,sageh,times]{sagej} % sage_latex_guidelines.tex V1.01, 11 June 2015
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts% This command is only needed if 
                                                          % you want to use the \thanks command
%\overrideIEEEmargins                                      % Needed to meet printer requirements.
\usepackage{times}

\makeatletter 
\let\NAT@parse\undefined
\makeatother

% numbers option provides compact numerical references in the text. 
%\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

\usepackage{bbm}
\usepackage{calc}
\usepackage{url}
\usepackage{transparent}
\usepackage{hyperref}
\hypersetup{
  colorlinks =false,
  urlcolor = black,
  linkcolor = black
}
\usepackage{graphicx}
\usepackage[cmex10]{amsmath}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{rotating}

\usepackage{chngcntr}
\counterwithin{paragraph}{subsection} % makes paragraph depend on subsection

%\usepackage{xfrac}
\usepackage{nicefrac}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage[usenames, dvipsnames]{color}
\usepackage{colortbl}
%\usepackage{caption}

%\usepackage{wrapfig}
\usepackage{overpic}
%\usepackage{subfigure}
%\usepackage{textcomp}
\graphicspath{{./pictures/pdf/},{./pictures/ps/},{./pictures/png/},{./pictures/jpg/}}
\usepackage{breqn} %for breaking equations automatically
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
%\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{todonotes}
\usepackage{authblk}

%\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \framebox{\begin{minipage}[c]{0.98 \columnwidth} \ttfamily\flushleft \textcolor{red}{#1}\end{minipage}}\vspace{5 mm}\par}
% uncomment this to hide all red todos
%\renewcommand{\todo}{}

%% ABBREVIATIONS
\newcommand{\qstart}{q_{\text{start}}}

%% MACROS

\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\providecommand{\normn}[2]{\left\lVert#1\right\rVert_#2}
\providecommand{\dualnorm}[1]{\norm{#1}_\ast}
\providecommand{\dualnormn}[2]{\norm{#1}_{#2\ast}}
\providecommand{\set}[1]{\lbrace\,#1\,\rbrace}
\providecommand{\cset}[2]{\lbrace\,{#1}\nobreak\mid\nobreak{#2}\,\rbrace}
\providecommand{\lscal}{<}
\providecommand{\gscal}{>}
\providecommand{\lvect}{\prec}
\providecommand{\gvect}{\succ}
\providecommand{\leqscal}{\leq}
\providecommand{\geqscal}{\geq}
\providecommand{\leqvect}{\preceq}
\providecommand{\geqvect}{\succeq}
\providecommand{\onevect}{\mathbf{1}}
\providecommand{\zerovect}{\mathbf{0}}
\providecommand{\field}[1]{\mathbb{#1}}
\providecommand{\C}{\field{C}}
\providecommand{\R}{\field{R}}
\newcommand{\Cspace}{\mathcal{Q}}
\newcommand{\Uspace}{\mathcal{U}}
\providecommand{\Fspace}{\Cspace_\text{free}}
\providecommand{\Hcal}{$\mathcal{H}$}
\providecommand{\Vcal}{$\mathcal{V}$}
\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\cone}{cone}
\DeclareMathOperator{\homog}{homog}
\DeclareMathOperator{\domain}{dom}
\DeclareMathOperator{\range}{range}
\DeclareMathOperator{\sign}{sgn}
\providecommand{\polar}{\triangle}
\providecommand{\ainner}{\underline{a}}
\providecommand{\aouter}{\overline{a}}
\providecommand{\binner}{\underline{b}}
\providecommand{\bouter}{\overline{b}}
\newcommand{\D}{\nobreakdash-\textsc{d}}
%\newcommand{\Fspace}{\mathcal{F}}
\providecommand{\Fspace}{\Cspace_\text{free}}
\providecommand{\free}{\text{\{}\mathsf{free}\text{\}}}
\providecommand{\iff}{\Leftrightarrow}
\providecommand{\subinner}[1]{#1_{\text{inner}}}
\providecommand{\subouter}[1]{#1_{\text{outer}}}
\providecommand{\Ppoly}{\mathcal{X}}
\providecommand{\Pproj}{\mathcal{Y}}
\providecommand{\Pinner}{\subinner{\Pproj}}
\providecommand{\Pouter}{\subouter{\Pproj}}
\DeclareMathOperator{\argmax}{arg\,max}
\providecommand{\Aineq}{B}
\providecommand{\Aeq}{A}
\providecommand{\bineq}{u}
\providecommand{\beq}{t}
\DeclareMathOperator{\area}{area}
\newcommand{\contact}[1]{\Cspace_{#1}}
\newcommand{\feasible}[1]{\Fspace_{#1}}
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\figwid}{0.22\columnwidth}
\newcommand{\TRUE}{\textbf{true}}
\newcommand{\FALSE}{\textbf{false}}
\DeclareMathOperator{\atan2}{atan2}
\allowdisplaybreaks

@@

%\setcounter{secnumdepth}{3}
%\runninghead{Shahrokhi \textit{et~al.}}
%\hyphenation{micro-robot nano-robot nano-robotics micro-robotics micro-robots nano-robots micro-manip-ulators}
%%%%%%%%%%%% For debugging purposes, I like to display the TOC
%    \tableofcontents
%    \setcounter{tocdepth}{3}
%    \newpage
%%%% END TOC %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{Shiva Shahrokhi, Chris Ertel, Mable Wan, Lillian Lin, Aaron T. Becker% end author block 
\thanks{Authors are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204 USA        {\tt\small  \{sshahrokhi2, atbecker\}@uh.edu}}
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}
\begin{abstract}
Microrobotics has the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges for controlling motion. We want to use large swarms of robots to perform manipulation tasks; unfortunately, human-swarm interaction studies as conducted today are limited in sample size, are difficult to reproduce, and are prone to hardware failures. We present an alternative.

@@

%\keywords{micro-robot, global control, swarm, human-swarm interaction}

@@

%\begin{dci}
%The Authors declare that there is no conflict of interest.
%\end{dci}
%\begin{funding}
%%RULES: http://www.nsf.gov/pubs/policydocs/pappguide/nsf16001/aag_6.jsp
%This work was supported by the National Science Foundation under Grant No.\ 
%\href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}.
%\end{funding}
%\newpage
%\begin{sm}
%\begin{itemize}
%\item Extension 1:  simulation video of the parameter sweeps in Fig.~\ref{fig:AutoVeryParam} with robot swarms manipulating objects.
%\item Extension 2: hardware experiment videos of object manipulation with a swarm of 100 kilobots.
%\end{itemize}
%\end{sm}

@@

\bibliographystyle{IEEEtran}
%\bibliographystyle{SageH}
\bibliography{IEEEabrv,SwarmControlIJRR}
